I've Got Nothing to Hide: \\ Exploring Privacy in Art, Books, and Film

### 2013-09-27 nothing_to_hide/presentation.tex
Working on beginning summary.

\begin{frame}
  \frametitle{Motivation}

  \begin{itemize}
  \item Tor runs on volunteers.
  \item Tor needs more volunteers.
  \item Tor should incentivize relay and bridge operators.
  \end{itemize}

  \begin{block}{People like money.}
    Provide incentives for Tor server operators through Bitcoin.
  \end{block}
\end{frame}

@@

@@

\end{frame}
\begin{frame}

\frametitle{\emph{Bleeding Edge} by Thomas Pynchon}

\begin{itemize}
\item Released last week
\item Very Pynchon.  Avant-garde literature ala \emph{Gravity's
  Rainbow}
\item Set in early 2001 in NYC.  In the post tech bust but before
  9/11.
\item Explores the idea of getting ``lost'' on the Internet and how
  that ended with 9/11.
\end{itemize}
\end{frame}

% \begin{frame}
% \frametitle{Survival Curve}
%   \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{survival}
% \end{frame}
%% \begin{frame}
%%   \frametitle{Bitcoin}

%%   Bitcoin is a peer-to-peer electronic currency based on
%%   proof-of-work. \cite{nakamoto2009bitcoin}

%%   \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{bitcoin_volume}

%% \end{frame}

%% \begin{frame}
%%   \frametitle{Can Bitcoin provide incentives?}

%%   Bitcoin is not
%%   anonymous.\cite{journals/iacr/AndroulakiKRSC12} \cite{journals/corr/abs-1107-4524}

%%   Combining Bitcoin as is with Tor would expose Tor users.  We seek to
%%   investigate alternative means of payments.
%%   \begin{itemize}
%%   \item Tor client joins a Bitcoin mining pool and payment goes
%%     directly to the Tor Server?
%%   \item Can we use Zerocoin? \cite{Miers:2013:ZAD:2497621.2498124}
%%     \end{itemize}

%%   \begin{block}{Anonymity}
%%     Tor incentives can't compromise anonymity!!
%%   \end{block}
%% \end{frame}

%% \begin{frame}
%%   \frametitle{Approach}

%%   \begin{itemize}
%%   \item Compare BitTor to other incentive
%%     systems.\cite{Jansen:2010:RNT:1866307.1866344}\cite{lira-ndss13}\cite{raykova-pet2008}
%%   \item Investigate Bitcoin payment methods.
%%   \item Provide anonymity analysis.
%%     \item Prototype BitTor and investigate performance

%%     \end{itemize}

%%   \begin{block}{Live and dynamic systems}
%%     Bitcoin = money, Tor = privacy $\rightarrow$ testing to be done ``offline.''
%%   \end{block}
%% \end{frame}

%% \begin{frame}[allowframebreaks]

%%   \frametitle{References}
%%   \begin{small}
%%   \phantomsection
%%   \addcontentsline{toc}{section}{\bibname}
%%   \bibliographystyle{acm}
%%   \bibliography{bitcoin,tor}
%%   \end{small}

%% \end{frame}

>>>>

\begin{frame}
  \frametitle{I've Got Nothing to Hide}

A brief summary of \emph{``I've Got Nothing to Hide'' and Other
  Misunderstandings of Privacy} by Daniel J. Solove.

\begin{itemize}
\item If you have nothing to hide, what do you have to fear?
\item More like, ``I don't care what happens, so long as it doesn't
  happen to me.''
\item Strongest argument has a utilitarian perspective: national
  security is more important than my privacy.

\end{itemize}
\end{frame}

\frametitle{Privacy is hard to define}

The taxonomy of privacy:

\begin{columns}[c] % the "c" option specifies center vertical alignment
    \column{.5\textwidth} % column designated by a command

    \begin{itemize}
    \item Information Collection
      \begin{itemize}
      \item Surveillance
      \item Interrogation
      \end{itemize}
    \item Information Processing
      \begin{itemize}
      \item Aggregation
      \item Identification
      \item Insecurity
      \item Secondary Use
      \item Exclusion
      \end{itemize}

    \column{.5\textwidth}

    \begin{itemize}
    \item Information Dissemination
      \begin{itemize}
      \item Breach of Confidentiality
      \item Disclosure
      \item Exposure
      \item Increased Accessibility
      \item Blackmail
      \item Appropriation
      \item Distortion
        \end{itemize}
    \item Invasion
      \begin{itemize}
      \item Intrusion
      \item Decisional Interference

\begin{columns}[c] % the "c" option specifies center vertical alignment
    \column{.5\textwidth} % column designated by a command

    \begin{block}{}
      Privacy in Art.
    \end{block}

    \column{.5\textwidth}

@@

\begin{columns}[c] % the "c" option specifies center vertical alignment
    \column{.5\textwidth} % column designated by a command

    \begin{block}{}
      Privacy in Fiction.
    \end{block}

    \column{.5\textwidth}

@@

\begin{columns}[c] % the "c" option specifies center vertical alignment
    \column{.5\textwidth} % column designated by a command

    \begin{block}{}
      Privacy in Film.
    \end{block}

    \column{.5\textwidth}

\begin{frame}
\frametitle{\emph{V for Vendetta} 2005}

\begin{columns}[c] % the "c" option specifies center vertical alignment
    \column{.5\textwidth} % column designated by a command
    \begin{itemize}

      \item Orwellian: state surveillance, mandatory curfews, state media.
      \item Popularized Guy Fawkes Masks.
      \item Banned books, art, and subversive material.
    \end{itemize}

    \includegraphics[width=\textwidth,height=0.6\textheight,keepaspectratio]{img/guy_fawkes}

    \column{.5\textwidth}
    \begin{figure}
    \includegraphics[width=\textwidth,height=0.6\textheight,keepaspectratio]{img/banned_books}
    %\caption{Me reading a banned book.  I would not do well in a
      %\emph{V for Vendetta} world.}
    \begin{block}{Caught with a banned book}
      I would not do well in a \emph{V for Vendetta} world.
    \end{block}
    \end{figure}

\begin{frame}
\frametitle{\emph{Das Leben der Anderen} (2006)}
\begin{columns}[c] % the "c" option specifies center vertical alignment
    \column{.5\textwidth} % column designated by a command
    \begin{itemize}

      \item 1950 - 1990 during the DDR, a \emph{real} surveillance
        state existed.
      \item Nearly every item on the taxonomy of privacy is violated.
      \item Stasi infiltration ran deep: industry, schools, and spouses.
    \end{itemize}

    \column{.5\textwidth}
    \begin{figure}
    \includegraphics[width=\textwidth,height=0.6\textheight,keepaspectratio]{img/stasi}
    %\caption{Me reading a banned book.  I would not do well in a
      %\emph{V for Vendetta} world.}

\begin{block}{Why invent dystopias?}
      History serves as a better example.
\end{block}

\begin{frame}
\frametitle{Discussion Ideas}

\begin{itemize}
\item Would you keep your blinds open in NYC if you lived there?  What
  if your neighbor was taking pictures?
\item When, if ever, would you consider filling a Freedom of
  Information Act (FOIA) request for your file?
\item The TSA back-scatter machines have raised privacy concerns
  because of the revealing images.  Would you / did you go throw them?
  Did you feel any pressure to choose the scanner over the pat-down?
